---
title: "Lab 01 - Hello R"
author: "Jamieson Nathan"
date: "1/17/2025"
output: github_document

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

- There are 1846 rows and 3 different variables (i.e., columns?) 
- The different variables are the data set identifier, x-values, and y-values

### Exercise 2

> dino_data <- datasaurus_dozen %>%
+     filter(dataset == "dino")
> ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
+     geom_point()

Plot makes a dinosaur! Unsure how to paste that in here...

And r = -0.0645

### Exercise 3


```{r plot-star}

```

```{r cor-star}

```
I noticed it made a star! Also the r value was a little higher but almost identical. 


### Exercise 4

Add your code and narrative to complete this exercise. Use the conventions from the previous exercises to name your chunks and organize your work.

```{r plot-circle}

circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

```{r cor-circle}


```
Value is identical (rouned) to dino. 

### Exercise 5

```{r plot-all}

ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset, ncol = 3) +
  theme(legend.position = "none")

```
```{r cor-all} 

datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)

```


